---
title:  Powerpoint from Rmarkdown
author: "Richard Martin"
date: "02/02/2022"
output: 
  powerpoint_presentation:
    reference_doc: aest_style.potx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggrepel)
library(DT)
car_data <- mtcars%>%
  rownames_to_column()
```

## Reproducible Research:

- Entire chain from raw data to output is documented/coded... no "by hand" modifications that are impossible to re-create.
- Ensures that changes to either data or methodology get automatically reflected in the output.
- The priority is on accuracy rather than aesthetics.

## Motortrend cars from 1974:
:::::: {.columns}
::: {.column}
```{r}
fastest <- car_data%>%
  filter(qsec==min(qsec))
ggplot(car_data, aes(hp,qsec,colour=wt))+
  geom_point()+
  geom_label_repel(data=fastest, mapping=aes(label=rowname))+
  scale_colour_viridis_c()+
  labs(x="Horsepower",
       y="Quarter mile time",
       colour="Weight")
```
:::
::: {.column}
- The fastest car is the `r fastest$rowname` which gets `r fastest$mpg` Miles per gallon, and has `r fastest$hp` horsepower.
:::
::::::
## Suppose Pantera is dropped (for some reason) 
:::::: {.columns}
::: {.column}
```{r, echo=TRUE, message=FALSE}
car_data <- anti_join(car_data,fastest)%>%
  arrange(qsec)
```
:::
::: {.column}
```{r}
datatable(car_data)
```
:::
::::::
## And run the same code again. 
:::::: {.columns}
::: {.column}
```{r, message=FALSE}
# exact same code.
fastest <- car_data%>%
  filter(qsec==min(qsec))
ggplot(car_data, aes(hp,qsec,colour=wt))+
  geom_point()+
  geom_label_repel(data=fastest, mapping=aes(label=rowname))+
  scale_colour_viridis_c()+
  labs(x="Horsepower",
       y="Quarter mile time",
       colour="Weight")
```
:::
::: {.column}
- Now there is a new fastest car, and the plot **and** the prose automatically reflect this.
- The fastest car is the `r fastest$rowname` which gets `r fastest$mpg` Miles per gallon, and has `r fastest$hp` horsepower.
:::
::::::

## Drawbacks:

- Any modifications to .ppt would be lost if the analysis had to be rerun.
- So no aesthetic modifications to ppt should be made until numbers finalized. 



